$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$

### 2020-03-16 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

originated from the same reaction vertex at the target (See Supplemental Material \cite{Suppl_Mat}).\\

@@

where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{\mathrm{rec}}$ is the recoil factor and $\sigma_{\mathrm{cc1}}$ is the de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.
$p_{\mathrm{r}}$ for three recoil angle settings at

@@

\begin{figure}[hb!]

@@

\noindent $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$. For the two highest settings ($p_{r}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{r}$ . The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). The good agreement between the Hall A and C data at lower $p_{r}$

>>>>

originated from the same reaction vertex at the target.\\

@@

where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K=E_{\mathrm{f}}p_{\mathrm{f}}$ is a kinem-

@@

\begin{figure}[ht!]

@@

\noindent atical factor, $f_{\mathrm{rec}}=\frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$ is the recoil factor and $\sigma_{\mathrm{cc1}}$ is the
de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.
$p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$. For the two highest settings ($p_{r}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{r}$ . The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). The good agreement between the Hall A and C data at lower $p_{r}$
